\documentclass{article}

\usepackage{titling}
\usepackage[margin=.8in]{geometry}
\usepackage{url}
\usepackage{alltt}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[us,12hr]{datetime}
\fancypagestyle{plain}{
\fancyhf{}
\rfoot{Last Compiled: {\mmddyyyydate\today} at \currenttime}
\lfoot{John Radford's Resume}
\renewcommand{\headrulewidth}{0pt}}
\pagestyle{plain}

\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{.5ex}{1ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

\pagenumbering{gobble}

\titleformat{\section}
{\huge\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries\Large}
{\hspace{-.10in}}
{0em}
{}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}[———————————]

\renewcommand{\maketitle}{
\begin{flushleft}
{\huge\bfseries
\theauthor}

\vspace{.25em}
\textbf{Email:} johnlradford23@gmail.com
\textbf{Website:} https://johnlradford.io 
\end{flushleft}
}
\vspace{0em}

\begin{document}

\title{R\'esum\'e}
\author{John L. Radford}

\maketitle

\section{Education}

\noindent
\textbf{University of Pittsburgh - Greensburg Campus (Graduated: 2017)}

Bachelor of Arts: Humanities Gen., Philosophy/Art History/Classical Literature

Minor: Political Science

\section{Work Experience}

\subsection{IT Helpdesk Assistant -- University of Pittsburgh Greensburg}

\noindent
\textbf{Timeframe: Spring \& Fall Semester 2017}

As a workstudy, I was responsible for assisting students and faculty with
computing issues, both in person and over the phone. Learned to work with
networking, printing, and AV equipment. Learned to resolve issues on Mac,
Windows, and mobile platforms.

\subsection{Security / Support Technician Lvl 2 -- Pair Networks, Inc.}

\noindent
\textbf{Timeframe: 2018 - 2023}

I started at Pair Networks as a support technician where I was responsible for
answering customer phone calls and Email tickets regarding issues with
websites, mailboxes, databases, DNS, ect. I was promoted quickly to several
teams including, Upgrades \& Moves, Urgent Live Server Monitoring \& Response,
Signup Fraud Detection, Abuse, and Security.

\subsection{Junior System Administrator -- Pair Networks, Inc.}

\noindent
\textbf{Timeframe: 2023 - Present}

I'm currently employed as a junior system administrator for Pair Networks where
I assist in overseeing the infrastructure necessary to provide world class web
hosting services!

\section{Sample Projects}

\noindent
\textbf{SSH Key Network Mapper -- \url{https://github.com/BlueSquare23/ssh-map}}

Created a simple Python utility to help enumerate \& map ssh key networks. Uses
the \emph{paramiko} SSHClient to enumerate key logins. Distributed JSON can then
be collected into a central \emph{SQLite} database then finally visualized
with 3rd party tools.

\noindent
\textbf{Reverse Shell Payload Generator -- \url{https://rshell.sh}}

Made a website / API using Python \emph{Flask} to facilitate the delivery of
reverse shell payloads from the cloud to your terminal or application. Setup
\emph{Pytest} unit testing and implemented homemade CD/CI pipeline for
production deployment.

\noindent
\textbf{Web LGSM -- \url{https://github.com/BlueSquare23/web-lgsm}}

Created a fully tested stand alone web portal for the
\href{https://linuxgsm.com/}{LGSM} game server manager with Python3 using the
\emph{Flask} web-framework, a \emph{SQLite} database, \emph{SQLAlchemy} as the
ORM, and \emph{Bootstrap 5} for nearly all of the CSS.

\section{Software, Languages, and Tools I Know}

FreeBSD, Linux, Android, Vim, Git, C, Bash, Perl, Python, PHP, Java,
JavaScript, TypeScript, JQuery, ReactJS, Vite, Nodejs, SQL, HTML, CSS, SASS,
Markdown, {\LaTeX}, Mediawiki Markdown, Flask, CGI, Bootstrap, WordPress,
MediaWiki, Apache, Nginx, Postfix, Dovecot, MySQL, Docker, QEMU/KVM,
VirtualBox, Ansible, Puppet and more. 

\section{Accolades}

\begin{itemize}
\setlength{\itemsep}{1pt}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\item Eagle Scout, Boy Scouts of America - Troop 66

\item Ex Pluribus Capitibus Supra of the UPG Campus Alliance for Free Thought

\item President of University of Pittsburgh's delegation to the model European Union (2016)
\end{itemize}

\end{document}
